\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-20 metatheory-condensed.tex
Save. Metatheory

However, there is subtle difference compared to the plugin implementation---$(\mu^+ ~o~\{f\}~t)$ reads as \textit{``$t$ is a new well-typed field when we abstract the \textbf{prior} fields using $f$''}. In other words, every field in meta-theory has a right to choose how they perceive and abstract the prior fields. While in the plugin, "Overridable" will decide how the current defining field is percived by the following fields.

@@

Similar to plugin implementation, we delegate handlers (and their inheritance structure) for recursion to linkages. We use "RecSig1" to compute the type of a single handler and "RecSig" for the complete family of handlers for all constructors. \ruleref{Rec-Constr} uses "RecSig" to achieve exhaustiveness checking on elimination. The partial recursors and the computational axioms are treated as normal fields as expected, since we know they are provable in the plugin implementation.

@@

\subsection{Relation to Plugin Implementation}
Our core calculus can model most of plugin implementation.

% Extending Inductive Type

% Focus on FRecursion and FInduction

% Partial Recursor + Computational Axiom
The partial recursors and the computational axioms are no different from recursors and normal fields. We can prove partial recursor using current recursing mechanism and proving computational axiom on the trivial abstraction. After that, we can use sealing to abstract partial recursor and computational axiom again for the later fields.

% Extending Recursion Handler
The extension of recursion handlers is delegated by the inheritance of families. Adding new handlers for a new constructors is exactly extending families with new fields of certain types.

% Overriding + Pins
Finally, we pointed out how overridable and pins is modeled.. Despite the fact we have a complicated dynamic of invisibility between overridable and normal fields in the plugin, every field can be elaborated into the (pseudo)-syntax form \\ \mintinline{Coq}{Field hiding {x, y, z ...} newfield := t...}  where every former field x,y,z,...  hide its definition when type-check t, and remaining former fields have their definition exposed in t.
This above elaborated "hiding" syntax directly corresponding to the semantic of sealing---when definition is exposed, we expose a term by using singleton type, which will provide us a judgemental equality to the definition.

>>>>

However, there is subtle difference compared to the plugin implementation---$(\mu^+ ~o~\{f\}~t)$ reads as \textit{``$t$ is a new well-typed field when we abstract the \textbf{prior} fields using $f$''}. In other words, every field in meta-theory has the right to choose how they perceive and abstract the prior fields. While in the plugin, "Overridable" keyword will decide how the current defining field is percived by the following fields.

We can now point out how "Overridable" and "pins" is modeled. Despite the fact we have a complicated dynamic of invisibility between overridable and normal fields in the plugin, every field can be elaborated into the (pseudo)-syntax form \\ \mintinline{Coq}{Field hiding {x, y, z ...} newfield := t...}  where every former field x,y,z,...  hide its definition when type-check t, and remaining former fields have their definition exposed in t.
This above elaborated "hiding" syntax directly corresponding to the $f$ in $(\mu^+ ~o~\{f\}~t)$, where each fields decides the abstraction of the prior.

@@

Similar to plugin implementation, we delegate handlers (and their reuse) for recursion to linkages (and their inheritance). We use "RecSig1" to compute the type of a single handler and "RecSig" for the complete family of handlers for all constructors. \ruleref{Rec-Constr} uses "RecSig" to achieve exhaustiveness checking on elimination. The partial recursors and the computational axioms are treated as normal fields as expected, since we know they are provable in the plugin implementation.

@@
